Lattice model

### 2017-04-03 oopsla17/lattice-model.tex
Remove definition of unused origin
Fix extended origin distance

\begin{defn}{(Extended origin)}
  In $N$-dimensions, the \emph{extended origin} is the interval
  $\interv{-1}{1}{N}$ contained in \region{N}.
\end{defn}

@@

  This notion extends to subscripts. Since there may be an infinite number of
  points, we measure the distance from the closest one.
\end{defn}
%
\begin{prop}{}
  The closed form of extend origin distance for an $N$-dimensional subscript $S$
  is denoted with $|S|$ and is defined as:
%
  \begin{align*}
    |S| & = \sum_{i=1}^{N} dist_i(S)
    &
    \textit{dist}_i(S) & = \begin{cases}
      0 & \pi_i(S) = \interv{-\infty}{\infty}{} \\
      |\mathsf{a}| - 1 & \pi_i(S) = \{\mathsf{a}\} \\
    \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
  \todo{%
    Not sure what we are going to prove here? That it is a metric space or
    something?

    Response: The definition says extended origin distance is the smallest
    number of translations to reach the extended origin, we need to prove that
    this formula indeed gives that.
  }
\end{proof}

>>>>

@@

  This notion extends to subscripts. Since there may be an infinite number of
  points, we measure the distance from the closest one.
\end{defn}
%
\begin{prop}{}
  The closed form of extend origin distance for an $N$-dimensional subscript $S$
  is denoted with $\mathit{dist}(S)$ and is defined as:
%
  \begin{align*}
    \mathit{dist}(S) & = \sum_{i=1}^{N} \mathit{dist}_i(S)
    &
    \mathit{dist}_i(S) & = \begin{cases}
      0 & \pi_i(S) = \interv{-\infty}{\infty}{} \\
      |\mathsf{a}| - 1 & \pi_i(S) = \{\mathsf{a}\} \\
    \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
  Now we prove that function $\mathit{dist}$ indeed gives the lowest number of
  unit translations to reach the extended origin.
\end{proof}
